Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-10 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Relate ND to the calculus of Benzmueller, Brown and Kohlhase

The natural deduction calculus used here has standard rules for propositional connectives and quantifiers, as shown in Figures \ref{fig:PropositionalRules} and \ref{fig:QuantifierRules}. The extension to classical logic is achieved by adding a rule for double negation elimination, shown in Figure \ref{fig:Classical}, and $\beta$-reduction is handled by the $\beta$ rule shown in Figure \ref{fig:ReductionRules}. Finally, modal operators are handled by special rules that insert or remove formulas from boxes, as shown in Figure \ref{fig:NDK}.
A \emph{derivation} is a directed acyclic graph whose nodes are formulas and whose edges correspond to applications of the inference rules. A \emph{proof} of a formula $F$ is a derivation without open assumptions and having $F$ as root not inside any box.

@@

The calculus having only the rules shown in Figures \ref{fig:PropositionalRules}, \ref{fig:Classical} and \ref{fig:QuantifierRules} is named \ND, while the calculus with the additional rules shown in Figure \ref{fig:NDK} is named \NDK.

@@

>>>>

The natural deduction calculus proposed and used here has standard rules for propositional connectives and quantifiers, as shown in Figures \ref{fig:PropositionalRules} and \ref{fig:QuantifierRules}. The extension to classical logic is achieved by adding a rule for double negation elimination, shown in Figure \ref{fig:Classical}, and $\beta$-reduction is handled by the $\beta$ rule shown in Figure \ref{fig:ReductionRules}.
Finally, modal operators are handled by special new rules that insert or remove formulas from boxes, as shown in Figure \ref{fig:NDK}.
A \emph{derivation} is a directed acyclic graph whose nodes are formulas and whose edges correspond to applications of the inference rules. A \emph{proof} of a formula $F$ is a derivation without open assumptions and having $F$ as root not inside any box.

@@

The calculus having only the rules shown in Figures \ref{fig:PropositionalRules}, \ref{fig:Classical} and \ref{fig:QuantifierRules} is named \ND. This calculus is essentially the same as the simplest natural deduction calculus in the family of calculi discussed in \citep{BenzmuellerBrownKohlhase}. The main difference is that they take disjunction as a primitive connective instead of conjunction, and they use a sequent notation, where the assumptions are listed in the left side of the sequent. The calculus with the new rules for modal operators shown in Figure \ref{fig:NDK} is named \NDK.

@@

\bibitem[{\itshape Benzm\"uller \& Brown \& Kohlhase(2004)}]{BenzmuellerBrownKohlhase}
Benzm\"uller, C. \& Brown C. \& Kohlhase, M. In: {\ishape Journal of Symbolic Logic}, Vol. 69, N. 4, pp. 1027--1088.
